\documentclass[a4paper]{exam}

\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}

\header{CS/MATH 113}{WC06: Logical Inference}{Spring 2024}
\footer{}{Page \thepage\ of \numpages}{}
\runningheadrule
\runningfootrule

\printanswers

\newcommand\cb{\color{blue}}
\newcommand\cre{\color{red}}
\newcommand\cg{\color{green}}
\newcommand\cy{\color{yellow}}
\newcommand\cgr{\color{gray}}

\title{Weekly Challenge 06: Logical Inference}
\author{CS/MATH 113 Discrete Mathematics}
\date{Spring 2024}

\qformat{{\large\bf \thequestion. \thequestiontitle}\hfill}
\boxedpoints

\begin{document}
\maketitle

\begin{questions}

  \titledquestion{Sacred Secrets}[5] Legend has it that one of the TAs from a previous offering of CS/MATH 113 prepared a manual, ``Sacred Secrets: How to Earn an A+ and Stay Sane''. However their own sanity is sadly no longer intact. The \LaTeX\ source and the repository got deleted and all that exists about the location of the only printed copy are the following instructions.
  \begin{enumerate}
  \item There is a hint at Learn Courtyard or at the Gym.
  \item If your TA is sitting in Ehsas or they are absent, then there is a hint at Learn Courtyard.
  \item If your TA is not sitting in Ehsaas, then there is a hint at the Gym.
  \item If there are people in Learn Courtyard, then there is no hint at Learn Courtyard.
  \item If there is a hint at Learn Courtyard, then the manual is at Zen Garden.
  \item If there is hint at the Gym, then the manual is at Earth Courtyard.
  \item If your TA is absent, then the manual is at Fire Courtyard.
  \end{enumerate}
  You notice that there are people in Learn Courtyard. Show how you can infer the location of the manual.

  \begin{solution}
    
    Since there are people in Learn Courtyard then according to the 4th statement there is no hint at Learn Courtyard. Since the hint is not at Learn Courtyard then according to statement 2, the TA is not sitting in EHSAS nor they are absent. Now that we know that TA is not in Ehsas, then statement 3 tell us that there is a hint at the gym. Statement 1 also confirms that the hint is at the gym because we have inferred that it is not at Learn Courtyard. Following 6, the manual is at Earth Courtyard.
    
  \end{solution}

\titledquestion{The Other Side} You are given four cards each of which has a number on one side and a letter on another. You place them on a table in front of you and the four cards read: \texttt{A 5 2 J}. Which cards would you turn over in order to test the following rule? Explain your choice.
      {\quotation Cards with 5 on one side have J on the other side.}

  \begin{solution}
    
    I would turn 5 to check if the card with 5 on the front has J on the back, if that is the case, then it must also be the case for every card with 5 to have J on back and vice versa.
    Additionally, I would turn A to check if the number on the back is 2. Since J is on the back of 5, then it must be the case that A is on the back of 2. This will confirm the rule.
  \end{solution}

  
\end{questions}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
